### 2022-03-29 pre/pre.tex
more

In practice, many implementations of $\lambda$-terms avoid named representation
of bound variables described above by using \emph{locally nameless
representation} \cite{ac-12-locally-nameless}. In this representation, free
variables retain their names, while abstractions are simply represented by a
$\lambda$ symbol, without any names. Further, bound variables are represented
using \emph{De Bruijn indices}. A bound variable with De Bruijn index
$\dbvar{i}$ is bound by the $i+1$-th enclosing $\lambda$-binder. For example,
the term $\lambda x. \cst{f} \, (\lambda y z. \cst{g} \, y \, x)$ is represented
as $\lambda\, \cst{f} \, (\lambda \lambda\, \cst{g} \, \db{0} \, \db{2})$.
Locally nameless representation reduces the $\alpha$-equivalence test to 
the syntactic equality test.

@@

\medskip
Let us give some intuition behind how these rules are applied in practice. The
\infname{ER} rule is used to replace equals by equals within a clause.
Consider the formula $\iforall x.\,  x \eq \cst{2} \iimplies \cst{even}(x)$. In
clausal form it is $X \noteq \cst{2} \llor \cst{even}(X)$. Applying the
\infname{ER} rule effectively applies the precondition $X \eq \cst{2}$ to the
conclusion $\cst{even}(X)$ to obtain $\cst{even}(\cst{2})$. The \infname{EF}
rule can be used to find instances of the clause that can be further simplified.
Consider the clause $\cst{f}(X) \eq \cst{a} \llor \cst{f}(Y) \eq \cst{a} \llor
\cst{p}(X, Y)$. Applying \infname{EF} to its first two literals yields $\cst{a}
\noteq \cst{a} \llor \cst{f}(X) \eq \cst{a} \llor \cst{p}(X, X)$ (with $\sigma = \{ Y \mapsto X \}$). This clause
then further simplifies to $\cst{f}(X) \eq \cst{a} \llor \cst{p}(X, X)$ using \infname{ER}.

>>>>

In practice, many implementations of $\lambda$-terms avoid named representation
of bound variables described above by using \emph{locally nameless
representation} \cite{ac-12-locally-nameless}. In this representation, free
variables retain their names, while abstractions are simply represented by a
$\lambda$ symbol, without any names. Further, bound variables are represented
using \emph{De Bruijn indices}. A bound variable with De Bruijn index
$\dbvar{i}$ is bound by the $i+1$-th enclosing $\lambda$ binder. For example,
the term $\lambda x. \, \cst{f} \, (\lambda y z. \, \cst{g} \, z \, x)$ is represented
as $\lambda\, \cst{f} \, (\lambda \lambda\, \cst{g} \, \db{0} \, \db{2})$.
Locally nameless representation reduces the $\alpha$-equivalence test to 
the syntactic equality test.

@@

\medskip
Note that with \emph{superposition rule} we refer to both \infname{SN} and \infname{SP}
rules.
Let us give some intuition behind how these rules are applied in practice. The
\infname{ER} rule is used to replace equals by equals within a clause.
Consider the formula $\iforall x.\,  x \eq \cst{2} \iimplies \cst{even}(x)$. In
clausal form it is $X \noteq \cst{2} \llor \cst{even}(X)$. Applying the
\infname{ER} rule effectively applies the precondition $X \eq \cst{2}$ to the
conclusion $\cst{even}(X)$ to obtain $\cst{even}(\cst{2})$. The \infname{EF}
rule can be used to find instances of the clause that can be further simplified.
Consider the clause $\cst{f}(X) \eq \cst{a} \llor \cst{f}(Y) \eq \cst{a} \llor
\cst{p}(X, Y)$. Applying \infname{EF} to its first two literals yields $\cst{a}
\noteq \cst{a} \llor \cst{f}(X) \eq \cst{a} \llor \cst{p}(X, X)$ (with $\sigma = \{ Y \mapsto X \}$). This clause
then further simplifies to $\cst{f}(X) \eq \cst{a} \llor \cst{p}(X, X)$ using \infname{ER}.
